manuscript_figures

### 2024-07-12 scripts/manuscript_figures.Rmd
updated HPI and fish production code

# Figure 3: organize and calculate kelp biomass data to make fish biomass/kelp biomass (g/m2) linear regression figure
```{r}
# read in quad data with filtered for just kelp
quad.filt <- QUAD %>%
  filter(SP_CODE == "SUGK" | SP_CODE == "LADI")

@@

#load in morph data and select for SUGK
morph.filt <- morph %>%
        filter(SP_CODE == "SL" | SP_CODE == "LADI")

@@

# Calculate fish biomass 'W' using the length-weight relationship
PB_filtered$Wmat <- PB_filtered$coef.a * (PB_filtered$Lmat^PB_filtered$coef.b)

@@

# Calculate fish biomass
PB_filtered$biomass <- PB_filtered$Wmat * PB_filtered$COUNT

# Calculate biomass per m²
PB_filtered$biomass_per_m2 <- PB_filtered$biomass / 80

>>>>

# Figure 3: organize and calculate kelp biomass data to make fish biomass/kelp biomass (g/m2) linear regression figure
```{r}
# read in quad data with filtered for just kelp
quad.filt <- QUAD %>%
  filter(SP_CODE == "SUGK" | SP_CODE == "SUGK.1")

@@

#load in morph data and select for SUGK
morph.filt <- morph %>%
        filter(SP_CODE == "SL")

@@

# Calculate fish weight at maturity using the length-weight relationship
PB_filtered$Wmat <- PB_filtered$coef.a * (PB_filtered$Lmat^PB_filtered$coef.b)

@@

# add an individual fish.mass column where we take (PB_filtered$coef.a * (PB_filtered$actual_size ^ PB_filtered$coef.b)
PB_filtered$ind.fish.mass <- (PB_filtered$coef.a * (PB_filtered$actual_size ^ PB_filtered$coef.b))

# Calculate fish biomass: coefa * actual size ^b * COUNT
PB_filtered$biomass <- PB_filtered$ind.fish.mass * PB_filtered$COUNT

# add total biomass for each transect per species
PB.aggregated <- PB_filtered %>%
  group_by(YEAR, SITE, TRANSECT, SP_CODE) %>%
  summarise(tot.biomass = sum(biomass, na.rm = TRUE),
            .groups = 'drop')

# Calculate biomass per m²
PB.aggregated$biomass_per_m2 <- PB.aggregated$tot.biomass / 80
